\texttt{MSnbase}, efficient and elegant R-based processing and visualisation of raw mass spectrometry data

### 2020-08-29 msnbase2.Rnw
fix typo

\textcolor{black}{The on-disk backend has become the preferred backend
  for large data, and the only viable alternative when the size of the
  data exceeds the available RAM and/or when several MS levels are to
  be loaded and handled simultaneously. The on-disk backend can still
  prove useful in cases when small MS2-only data are to be analysed
  and will remain available in future versions of \texttt{MSnbase}.}

>>>>

\textcolor{black}{The on-disk backend has become the preferred backend
  for large data, and the only viable alternative when the size of the
  data exceeds the available RAM and/or when several MS levels are to
  be loaded and handled simultaneously. The in-memory backend can
  still prove useful in cases when small MS2-only data are to be
  analysed, and will remain available in future versions of
  \texttt{MSnbase}.}
